---
title       : Computing the probability to survive on Titanic
subtitle    : Course Project
author      : Stepan Goncharov
job         : sociologist
framework   : io2012      # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Why is it interesting?

1. All people have different capabilities and resources to handle difficult situations.
2. This fact lies into the basis of modern society organization: how organized public spaces and transport, for example.
3. And analyzing such a tragic disaster like Titanic destraction helps to prevent them in future.

--- .class #id 

## Some preprocessing

Loading necessary data
```{r, results='asis', echo=F, message=F, warning=F}
library(lattice)
library(titanic)
library(Hmisc)
library(plyr)
```

```{r}
test <- titanic_test[,c("Pclass", "Sex", "Age")]
train_all <- titanic_train[,c("Pclass", "Sex", "Age")]
all <- rbind(test, train_all)
all$Age <- round(all$Age, 0)
all$age_groups <- cut2(all$Age, g=4)
all$Sex <- as.factor(all$Sex)
all$Pclass <- as.factor(all$Pclass)
```

```{r, echo=FALSE}
```
--- .class #id 

## Who travelled?

```{r, echo=F, cache=T}
histogram(~Pclass | Sex*age_groups, data = all, scales = list(x = list(labels = c("1 class", "2 class", "3 class"))), xlab = "Passenger Class", main = "Passanger classes by socio-demographic characteristics")
```

--- .class #id 

## My application
My applications builds GLM binomial model in data presented in titanic dataset.
```{r, echo=F}
train <- titanic_train[,c("Survived", "Pclass", "Sex", "Age")]
train$Survived <- as.factor(train$Survived)
train$Pclass <- as.factor(train$Pclass)
train$Sex <- as.factor(train$Sex)

fit <- glm(Survived ~ Age + Sex + Pclass, data = train, family = "binomial")
```
- Confidence Inteval & Coefficients
```{r, echo=T, message=F}
exp(confint(fit))
exp(fit$coefficients)
```
```{r, echo=F}
```

--- .class #id 

## Did these charectiristics really influence?

```{r, echo=F, results='asis'}
train$age_groups <- cut2(train$Age, g=4)
train$Survived <- revalue(train$Survived, c("0" = "Not survived", "1" = "Survived"))
histogram(~Pclass | Sex*Survived, data = train, scales = list(x = list(labels = c("1 class", "2 class", "3 class"))), xlab = "Passenger Class", main = "Who survived")
```